The Impact of Anthropogenic Forcing on ENSO Amplitude

### 2021-10-31 presentations/presentation/presentation.tex
more stuff woohoo

\usepackage{natbib}
\usepackage{tikz}
\usepackage{varwidth}

@@

\begin{frame}{Climate forcing}
  \begin{columns}
    \column{0.5\textwidth}
    \begin{itemize}
    \item \alert{Forcing}: any external factor that affects climate.
      \begin{description}
      \item[\alert{GHG}] Greenhouse gasses
      \item[\alert{AER}] Aerosols (natural: volcanic ash, artificial: smoke)
      \item[\alert{BMB}] Biomass burning
      \item[\alert{LULC}] Land use/cover (deforestation, desertification)
      \end{description}
    \end{itemize}
    \column{0.6\textwidth}
    \myfig{greenhouse_Effect.jpg}{Factors that contribute to the greenhouse effect.}{this}
  \end{columns}
\end{frame}

@@

\begin{frame}{Wavelet Analysis}
  \begin{columns}
    \column{0.6\textwidth}
    \begin{itemize}
    \item Separate ENSO record into frequency over time.
    \item Increase in power in late 21\textsuperscript{st} century agrees with previous results.
    \item CESM2 shows a slight ``speeding up'' of ENSO as period decreases in late 21\textsuperscript{st} century.
    \end{itemize}
    \column{0.6\textwidth}
    \myfig{wavelet2.pdf}{Wavelet power spectrum for the Niño 3.4 index in the fully-forced CESM1 and CESM2 ensembles}{wavelet2}
  \end{columns}
\end{frame}

>>>>

\usepackage{natbib}
\usepackage{tikz}
\usepackage{varwidth}
\usepackage{hyperref}

@@

\begin{frame}{Climate forcing}
  \begin{columns}
    \column{0.5\textwidth}
    \begin{itemize}
    \item \alert{Forcing}: any external factor that affects climate.
      \begin{description}
      \item[\alert{GHG}] Greenhouse gasses
      \item[\alert{AER}] Aerosols (natural: volcanic ash, artificial: smoke)
      \item[\alert{BMB}] Biomass burning
      \item[\alert{LULC}] Land use/cover (deforestation, desertification)
      \end{description}
    \end{itemize}
    \column{0.6\textwidth}
    \myfig{greenhouse_Effect.jpg}{Factors that contribute to the greenhouse effect. \url{https://www.coolaustralia.org/the-greenhouse-effect-secondary}}{this}
  \end{columns}
\end{frame}

@@

\begin{frame}{Wavelet Analysis}
  \begin{columns}
    \column{0.6\textwidth}
    \begin{itemize}
    \item Separate ENSO record into frequency over time.
    \item Increase in power in late 21\textsuperscript{st} century agrees with previous results.
    \end{itemize}
    \column{0.6\textwidth}
    \myfig{wavelet2.pdf}{Wavelet power spectrum for the Niño 3.4 index in the fully-forced CESM1 and CESM2 ensembles}{wavelet2}
  \end{columns}
\end{frame}
